---
title: "R Markdown Presentation & Plotly"
author: "TSAI  YI- FAN"
date: "2018/4/23/"
output:
  html_document:
    keep_md: yes
  pdf_document: default
---

Instructions
=============
These are the aspect that we will be covering with the presentation:
This introduction in which we are dealing with rmarkdown
1. A second one in which run R code inside the slide.
2. And finally we will draw a chart with plotly.


```{r echo = TRUE}
 library(plotly)
```

Loading required package: ggplot2
=====================
Attaching package: ‘plotly’
The following object is masked from ‘package:ggplot2’:
last_plot
The following object is masked from ‘package:stats’:
filter
x The following object is masked from ‘package:graphics’:
layout

```{r echo = TRUE}
data(iris)
head(iris)
```

```{r echo = TRUE}
plot_ly(x= iris$Sepal.Width, y= iris$Sepal.Length, z = iris$Species, 
type = "scatter3d", mode = "markers", color = iris$Species)
```
Warning in arrange_impl(.data, dots): ‘.Random.seed’ is not an integer
vector but of type ‘NULL’, so ignored
=================